
---
title: "CASA0023 Week 2 slides"
subtitle: "⚔<br/>with xaringan"
author: "Tongmeng Xie"
institute: "CASA, UCL"
date: "January 19th, 2023 (updated: `r Sys.Date()`)"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---


```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

---

class: inverse, center, middle

# Get Started

------------------------------------------------------------------------

# Hello Ninja

Install the **xaringan** package from [Github](https://github.com/yihui/xaringan):

```{r eval=FALSE, tidy=FALSE}
remotes::install_github("yihui/xaringan")
```

--

You are recommended to use the [RStudio IDE](https://www.rstudio.com/products/rstudio/), but you do not have to.

-   Create a new R Markdown document from the menu `File -> New File -> R Markdown -> From Template -> Ninja Presentation`;<sup>1</sup>

--

-   Click the `Knit` button to compile it;

--

-   or use the [RStudio Addin](https://rstudio.github.io/rstudioaddins/)<sup>2</sup> "Infinite Moon Reader" to live preview the slides (every time you update and save the Rmd document, the slides will be automatically reloaded in RStudio Viewer.

.footnote\[ \[1\] 中文用户请看[这份教程](https://slides.yihui.org/xaringan/zh-CN.html)

\[2\] See [#2](https://github.com/yihui/xaringan/issues/2) if you do not see the template or addin in RStudio. \]

---

# Using Xaringan
.pull-right

---
# Data loading
```{r eval=FALSE, tidy=FALSE}
library(sf)
library(terra)
library(raster)
#library(dplyer)
library(magrittr)
library(tidyverse)

bare_earth <- st_read("prac_1/Data/Bare_earth_Polygon.shp")
grass <- st_read("prac_1/Data/Grass_Polygon.shp")
forest <- st_read("prac_1/Data/Forest_Polygon.shp")
urban <- st_read("prac_1/Data/Low_urban_Polygon.shp")
high_urban <- st_read("prac_1/Data/High_urban_Polygon.shp")

#Landsat equivalent
bands <- c("1","2", "3", "4", "5", "6", "7")

sentinel <- rast("prac_1/Data/S2A_LSAT_msk.tif")

names(sentinel) <- bands
  
landsat<-rast("prac_1/Data/LSAT_msk.tif")

names(landsat) <- bands

# make a SpatVector
urban <- terra::vect(urban)

# landsat to Raster
landsat <- as(landsat, "Raster")
```

# do this straight from loading the data with the pipe
```{r eval=FALSE}
bare_earth <- st_read("prac_1/Data/Bare_earth_Polygon.shp") %>%
  vect()
grass <- st_read("prac_1/Data/Grass_Polygon.shp")%>%
    vect()
forest <- st_read("prac_1/Data/Forest_Polygon.shp")%>%
    vect()
urban <- st_read("prac_1/Data/Low_urban_Polygon.shp")%>%
    vect()
high_urban <- st_read("prac_1/Data/High_urban_Polygon.shp")%>%
    vect()
```

---
# Data wrangling
## messing with crs and projection
```{r eval=FALSE}
crs(landsat)
crs(sentinel)

# reproject landsat
landsat <- project(landsat, sentinel)
```
## get the mean and standard deviation
```{r eval=FALSE}
band_fun <- function(sensor, landcover) { # sensor e.g. sentinel; landcover e.g. urban
  col_sensor <- deparse(substitute(sensor))
  col_land <- deparse(substitute(landcover))

  sen_urban<- terra::extract(sensor, landcover, progress = F)%>%
    as_tibble()%>%
    pivot_longer(cols = 2:7, 
               names_to="bands", 
               values_to="band_values")%>%
    add_column(sensor=col_sensor)%>%
    add_column(land=col_land)
                 
}

band_fun_all_values <- function(sensor, landcover) {
  col_sensor <- deparse(substitute(sensor))
  col_land <- deparse(substitute(landcover))

  sen_urban<- terra::extract(sensor, landcover, progress = F)%>%
    as_tibble()%>%
    pivot_longer(cols = 2:7, 
               names_to="bands", 
               values_to="band_values")
                 
}

# extract bands
sen_bare <- band_fun(sentinel, bare_earth)
sen_grass<- band_fun(sentinel, grass) 
sen_forest<- band_fun(sentinel, forest) 
sen_high_urban <- band_fun(sentinel, high_urban) 

lsat_urban<- band_fun(landsat, urban)
lsat_bare<- band_fun(landsat, bare_earth)
lsat_grass<- band_fun(landsat, grass)
lsat_forest<- band_fun(landsat, forest)
lsat_high_urban <- band_fun(sentinel, high_urban) 

# put into a tibble
sen_lsat <- bind_rows(sen_urban, sen_bare, sen_grass,
                      sen_forest, sen_high_urban,
                      lsat_urban, lsat_bare, lsat_grass,
                      lsat_forest, lsat_high_urban)
# get the mean (and standard deviation) values for each band per sensor and land cover type
means<- sen_lsat%>%
  group_by(bands, sensor, land)%>%
  summarise(Mean=mean(band_values), Std=sd(band_values))
```
---
# Ploting
```{r eval=FALSE}
# spectral profiles, first for Sentinel
p1 <- means %>%
  filter(sensor=="sentinel") %>%
  ggplot(., aes(x = bands, y = Mean,
                col=land))+
  geom_point()+
  geom_line(aes(group = land)) +
  geom_errorbar(aes(ymin = (Mean-Std), ymax = (Mean+Std), width = 0.2))
p1

# We can also look at a density plot (historgram for each land cover)
p2 <- sen_lsat %>%
  filter(sensor=="sentinel") %>%
ggplot(., aes(x=band_values, group=land, fill=land)) + 
  geom_density(alpha = 0.6)+
#Add a mean vertical line
  geom_vline(data = . %>% group_by(land) %>% summarise(group_mean = mean(band_values)),
             aes(xintercept=group_mean, color = land), linetype="dashed", size=1)

p2

# save
ggsave("spectral_reflectance.pdf", width = 20, height = 20, units = "cm")

# t-test
t1<- sen_lsat %>%
           filter(sensor=="sentinel" & land =="urban")%>%
           select(band_values)%>%
           pull()

t2<- sen_lsat %>%
           filter(sensor=="landsat" & land =="urban")%>%
           select(band_values)%>%
           pull()

t.test(t1, t2)
```


---
# Spatial signature on vegetation classification


---
# Spatial signature on 

---
# R

---
# Thanks!

Slides created via the R package [**xaringan**](https://github.com/yihui/xaringan).

The chakra comes from [remark.js](https://remarkjs.com), [**knitr**](https://yihui.org/knitr/), and [R Markdown](https://rmarkdown.rstudio.com).
